\chapter{Applications}
\label{chapt:apps}
\index{Applications}
\index{MARF!Applications}

$Revision: 1.18 $

This chapter describes the applications that employ {\marf}
for one purpose or another. Most of them are our own applications
that demonstrate how to use various {\marf}'s features. Others
are either research or internal projects of their own. If you
use {\marf} or its derivative in your application and would like
to be listed here, please let us know at \url{marf-devel@sf.lists.net}.


%
% Internal Research Applications
%

\section{MARF Research Applications}
\index{MARF!Research Applications}

%
% SpeakerIdentApp
%

\subsection{SpeakerIdentApp - Text-Independent Speaker Identification Application}
\index{Applications!SpeakerIdentApp}
\index{Research Applications!SpeakerIdentApp}

\api{SpeakerIdentApp} is an application for text-independent
speaker identification that exercises the most of the {\marf}'s
features.
\api{SpeakerIdentApp} is broadly presented through
the rest of this manual.


%
% ZipfLawApp
%

\input{zipf-law-app}


%
% LangIdentApp
%

\input{lang-ident-app}


%
% ProbabilisticParsingApp
%

\input{probabilistic-parsing-app}


%
% Internal Testing Applications
%

\section{MARF Testing Applications}
\index{MARF!Testing Applications}

%
% TestFilters
%

\input{test-filters}


%
% TestLPC
%

\input{test-lpc}


%
% TestFFT
%

\input{test-fft}


%
% TestWaveLoader
%

\input{test-wave-loader}


%
% TestLoaders
%

\input{test-loaders}


%
% MathTestApp
%

\input{math-test-app}


%
% TestPlugin
%

\input{test-plugin}


%
% TestPlugin
%

\input{test-nn}


%
% External Applications
%

\section{External Applications}
\index{MARF!External Applications}

%
% GIPSY
%

\subsection{GIPSY}
\index{Applications!GIPSY}
\index{External Applications!GIPSY}

{\gipsy} stands for General Intensional Programming System \cite{gipsy}, which is
a distributed research, development, and investigation platform about intensional and hybrid
programming languages. {\gipsy} is a world on its own developed at Concordia University and
for more information on the system please see \cite{gipsy} and \cite{mokhovmcthesis05}.
{\gipsy} makes use of a variety of {\marf}'s utility and storage modules, as of this
writing this includes:

\begin{itemize}
\item
	\api{BaseThread} for most threading part of the {\gipsy} for multithreaded
	compilation and execution.
\item
	\api{ExpandedThreadGroup} to group a number of compiler or executor threads
	and have a group control over them.
\item
	\api{Debug} for, well, debugging
\item
	\api{Logger} to log compiler and executor activities
\item
	\api{StorageManager} for binary serialization
\item
	\api{OptionProcessor} for option processing in five core {\gipsy} utilities
\item
	\api{Arrays} for common arrays functionality
\end{itemize}

There is a provision to also use {\marf}'s NLP modules.


%
% ENCSAssetsDesktop
%

\subsection{ENCSAssetsDesktop}
\label{sect:encs-assets-desktop}
\index{Applications!ENCSAssetsDesktop}
\index{External Applications!ENCSAssetsDesktop}

This is a private little application developed for the Engineering and Computer Science
faculty of Concordia University's Faculty Information Systems team. The application
synchronize inventory data between a Palm device database and a relational database
powering an online inventory application. This application primarily exercises:

\begin{itemize}
\item
    \api{BaseThread} for most threading part of the {\gipsy} for multithreaded
    compilation and execution.
\item
    \api{ExpandedThreadGroup} to group a number of compiler or executor threads
    and have a group control over them.
\item
    \api{Arrays} for common arrays functionality
\item
	\api{ByteUtils} for any-type-to-byte-array-and-back conversion.
\end{itemize}


%
% ENCSAssets
%

\subsection{ENCSAssets}
\index{Applications!ENCSAssets}
\index{External Applications!ENCSAssets}

This is a web frontend to an inventory database developed by the same team as
in \xs{sect:encs-assets-desktop}. It primarily exercises the threading
and arrays parts of {\marf}, namely \api{BaseThread} and \api{Arrays}.

%
% ENCSAssetsCron
%

\subsection{ENCSAssetsCron}
\index{Applications!ENCSAssetsCron}
\index{External Applications!ENCSAssetsCron}

This is a cron-oriented frontend to an inventory database developed by the same team as
in \xs{sect:encs-assets-desktop}. It primarily exercises the \api{OptionProcessor}
of {\marf}.

% EOF
