\section{Brief History of MARF}
\index{MARF!History}

$Revision: 1.13 $

The {\marf} project was initiated in September 26, 2002 by four students of
Concordia University, Montr\'eal, Canada as their course project for Pattern Recognition under
guidance of Dr. C.Y. Suen. This included Ian Cl\'ement, Stephen Sinclair,
Jimmy Nicolacopoulos, and Serguei Mokhov.

\subsection{Developers Emeritus}

\begin{itemize}
\item
Ian's primary contributions were the
LPC and Neural Network algorithms support with the \api{Spectrogram} dump.

\item
Steve has done an extensive
research and implementation of the FFT algorithm for feature extraction
and filtering and Euclidean Distance with the \api{WaveGrapher} class.

\item
Jimmy was focused on implementation of the WAVE file format
loader and other storage issues.

\item
Serguei designed the entire MARF framework and architecture,
originally implemented general distance classifier and its Chebyshev, Minkowski,
and Mahalanobis incarnations along with normalization of the sample data. Serguei
designed the Exceptions Framework of MARF and was involved into the integration
of all the modules and testing applications to use {\marf}.
\end{itemize}

\subsection{Contributors}

\begin{itemize}
\item
	Shuxin `Susan' Fan contributed to development and maintenance of some test applications
	(e.g. \api{TestFilters}) and initial adoption of the JUnit framework \cite{junit} within {\marf}.
	She has also finalized some utility modules (e.g. \api{marf.util.Arrays})
	till completion and performed {\marf} code auditing and ``inventory''.
	Shuxin has also added NetBeans project files to the build system of {\marf}.

\end{itemize}

\subsection{Current Status and Past Releases}

Now it's a project on its own, being maintained and developed as we have some spare time for it.
When the course was over, Serguei Mokhov is the primary maintainer of the
project. He rewrote \api{Storage} support and polished all of {\marf} during
two years and added various utility modules and NLP support and implementation of new
algorithms and applications. Serguei maintains this manual, the web site and most of
the sample database collection. He also made all the releases of the project
as follows:

\begin{itemize}
\item 0.3.0-devel-20060226 (0.3.0.5), Sunday, February 26, 2006
\item 0.3.0-devel-20050817 (0.3.0.4), Wednesday, August 17, 2005
\item 0.3.0-devel-20050730 (0.3.0.3), Saturday, July 30, 2005
\item 0.3.0-devel-20050606 (0.3.0.2), Monday, June 6, 2005
\item 0.3.0-devel-20040614 (0.3.0.1), Monday, June 14, 2004
\item 0.2.1, Monday, February 17, 2003
\item 0.2.0, Monday, February 10, 2003
\item 0.1.2, December 17, 2002 - Final Project Deliverable
\item 0.1.1, December 8, 2002 - Demo
\end{itemize}

\noindent
The project is currently geared towards completion planned TODO items on {\marf} and
its applications.

% EOF
