\chapter{Introduction}
\index{MARF!Introduction}

$Revision: 1.22 $

\section{What is MARF?}

{\marf} stands for {\bf M}odular {\bf A}udio {\bf R}ecognition {\bf F}ramework.
It contains a collection of algorithms for Sound, Speech, and Natural Language
Processing arranged into an uniform framework to facilitate addition of new
algorithms for preprocessing, feature extraction, classification, parsing, etc.
implemented in Java.
{\marf} is also a research platform for various performance metrics of the
implemented algorithms.

\subsection{Purpose}
\index{MARF!Purpose}

Our main goal is to build a general open-source framework to allow developers in the
audio-recognition industry (be it speech, voice, sound, etc.) to choose and apply various methods,
contrast and compare them, and use them in their applications. As a proof of concept, a
user frontend application for Text-Independent (TI) Speaker Identification has
been created on top of the framework (the \api{SpeakerIdentApp} program). A variety
of testing applications and applications that show how to use various aspects of {\marf}
are also present. A new recent addition is some (highly) experimental NLP support, which is also
included in {\marf} as of 0.3.0-devel-20050606 (0.3.0.2). For more information on applications
that employ {\marf} see \xc{chapt:apps}.

\subsection{Why {\java}?}

We have chosen to implement our project using the Java programming language. This
choice is justified by the binary portability of the Java applications as well as
facilitating memory management tasks and other issues, so we can concentrate more on
the algorithms instead. Java also provides
us with built-in types and data-structures to manage
collections (build, sort, store/retrieve) efficiently \cite{javanuttshell}.

\input{notation}

\section{Authors, Contact, and Copyright Information}
\index{MARF!Contact}
\index{MARF!Copyright}

\input{legal}

\subsection{Authors}
\index{MARF!Authors}

\noindent
Authors Emeritus, in alphabetical order:
\index{MARF!Authors Emeritus}

\begin{itemize}
	\item Ian Cl\'ement, \url{iclement@users.sourceforge.net}
	\item Serguei Mokhov, \url{mokhov@cs.concordia.ca}, a.k.a Serge
	\item Dimitrios Nicolacopoulos, \url{pwrslave@users.sourceforge.net}, a.k.a Jimmy
	\item Stephen Sinclair, \url{radarsat1@users.sourceforge.net}, a.k.a. Steve, radarsat1
\end{itemize}

\noindent
Contributors:
\index{MARF!Contributors}

\begin{itemize}
	\item Shuxin Fan, \url{fshuxin@gmail.com}, a.k.a Susan
\end{itemize}

\noindent
Current maintainers:
\index{MARF!Current maintainers}

\begin{itemize}
	\item Serguei Mokhov, \url{mokhov@cs.concordia.ca}
\end{itemize}

\noindent
If you have
some suggestions, contributions to make, or for bug reports, don't
hesitate to contact us :-)
For {\marf}-related issues please contact us at \url{marf-devel@lists.sf.net}.
Please report bugs to \url{marf-bugs@lists.sf.net}.

%
%
%

\input{history}

%
%
%

\input{sources}

%
%
%

\section{Versioning}
\index{Versioning}
\index{MARF!Versioning}

This section attempts to clarify versioning scheme employed
by the {\marf} project for stable and development releases.

In the 0.3.0 series a four digit version number was introduced
like 0.3.0.1 or 0.3.0.2 and so on. The first digit indicates
a {\em major version}. This typically indicates a significant
coverage of implementations of major milestones and improvements,
testing and quality validation and verification to justify a major
release. The {\em minor version} has to do with some smaller
milestones achieved throughout the development cycles.
It is a bit subjective of what the minor and major version bumps are, but
the TODO list in \xa{appx:todo} sets some tentative milestones
to be completed at each minor or major versions. The {\em revision}
is the third digit is typically applied to stable releases if there
are a number of critical bug fixes in the minor release, it's revision
is bumped. The last digit represents the {\em minor revision} of the
code release. This is typically used throughout development releases
to make the code available sooner for testing. This notion was first
introduced in 0.3.0 to count sort of increments in {\marf} development,
which included bug fixes from the past increment and some chunk of new
material. Any bump of major, minor versions, or revision, resets the
minor revision back to zero. In the 0.3.0-devel release series these
minor revisions were publicly displayed as dates (e.g. 0.3.0-devel-20050817)
on which that particular release was made.

All version as of 0.3.0 can be programmatically queried for
and validated against. In 0.3.0.5, a new \api{Version} class
was introduced to encapsulate all versioning information and
some validation of it to be used by the applications.

\begin{itemize}
\item
	the major version can be obtained from \api{marf.MARF.MAJOR\_VERSION}
	and \api{marf.Version.MAJOR\_VERSION} where as of 0.3.0.5 the former
	is an alias of the latter

\item
	the minor version can be obtained from \api{marf.MARF.MINOR\_VERSION}
	and \api{marf.Version.MINOR\_VERSION} where as of 0.3.0.5 the former
	is an alias of the latter

\item
	the revision can be obtained from \api{marf.MARF.REVISION}
	and \api{marf.Version.REVISION} where as of 0.3.0.5 the former
	is an alias of the latter

\item
	the minor revision can be obtained from \api{marf.MARF.MINOR\_REVISION}
	and \api{marf.Version.MINOR\_REVISION} where as of 0.3.0.5 the former
	is an alias of the latter
\end{itemize}

The \api{marf.Version} class provides some API to validate the version
by the application and report mismatches for convenience. See the API
reference for details. One can also query a full \api{marf.jar} or 
\api{marf-debug.jar} release for version where all four components
are displayed by typing:

\begin{verbatim}
    java -jar marf.jar --version
\end{verbatim}

% EOF
