\subsection{TestLoaders}
\index{Applications!TestLoaders}
\index{Testing Applications!TestLoaders}

$Revision: 1.4 $

\api{TestLoaders} is another testing applications of {\marf}.
It generalizes the testing machinery of \api{TestWaveLoader} for 
all possible loaders we may have. For now, it tests functionality of
the \api{WAVLoader} and \api{SineLoader} of {\marf}, the only two
implemented loaders; the others give non-implemented exceptions instead. 

From user's point of view, \api{TestLoaders} provides with usage, loader types, input sample, output
sample, and output textual file command-line options.
By entering \texttt{--help}, or \texttt{-h}, or when there are no arguments, the usage information will be displayed.
Entering \texttt{--version}, the \api{TestLoaders}' version and {\marf}'s version is displayed.
The usage info explains the arguments used in \api{TestLoaders}.
The first argument is a type of loader that is a mandatory argument.
The second argument is input file name that is mandatory for all loaders except for \api{SineLoader}.
The third and forth arguments are the output wave sample file and output textual sample file names of the loaded 
input sample. The names of the output files are optional arguments. If user does not provide any or both of
the last two arguments, the output files will be saved in the file names derived from the original.

\noindent
Complete usage information:

\vspace{15pt}
\hrule
\input{test-loaders-usage}
\hrule
\vspace{15pt}

The application is made to exercise the following {\marf} modules.
The main modules for testing are in the \api{marf.Storage.Loaders} package.
The \api{OptionProcessor} module in the \api {marf.util} helps handling the different loader types according
to the users input argument. The \api{Sample} and the \api{SampleLoader} modules in the \api{marf.Storage} help \api{WAVLoader} 
prepare loading input files. \api{Sample} maintains and processes incoming sample data. \api{SampleLoader}
provides sample loading interface for all the {\marf} loaders. It must be overridden by a concrete sample loader.
The modules work together to load in and write back a sample,
and save the loaded sample into a file, to save loaded input data into a data file referenced by \texttt{oDatFile}, 
and to output sample's duration and size to STDOUT. While for loading sine samples, it needs \api{SineLoader} implementation,
and instead of saving data file, it saves a csv file referenced by \texttt{oDatFile}.

The output of \api{TestLoaders} saves the loaded wave sample in a newly named output wave file.
Its output also saves the input file data into a textual file.
\api{TestLoaders} gives both users and programmers direct information of the results of MARF loaders.
Input sample can be compared with the expected output in the \file{expected} folder to detect any errors.

% EOF
